Scikit-learn: API design for machine learning

### 2013-06-17 paper.tex
shorter title
TODO still just over one line, must use smaller title font
Capitalize first letter (as we do in the JMLR paper)
remove \textit in subtitles
title

% working title, please change
\title{Python as a machine learning language:
       experiences from the scikit-learn project}

@@

\begin{abstract}
The \sklearn project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe the simple and elegant interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and analyzes obstacles faced by users
and developers of the library.
\end{abstract}

@@

\subsection{Extending \sklearn}

>>>>

% working title, please change
\title{Scikit-learn: API design for machine learning}

@@

\begin{abstract}
The \sklearn project is an increasingly popular open source machine learning
library written in Python and designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this paper, we present and
discuss our design choices for the application programming interface (API) of
the project. In particular, we describe the simple and elegant interface shared
by all learning and processing units in the library and then discuss its
advantages in terms of composition and reusability. The paper also comments on
implementation details specific to the Python ecosystem and analyzes obstacles
faced by users and developers of the library.
\end{abstract}

@@

\subsection{Extending scikit-learn}
